\documentclass{article}
\usepackage{fontawesome5}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[dvipsnames]{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage[sf]{libertine}
\usepackage{geometry}
\usepackage{supertabular}

\geometry{a4paper}
\fontsize{12pt}{15pt}\selectfont
\setlength\parindent{0pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Color definitions
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\definecolor{primary-50}{HTML}{fafaf9} 
\definecolor{primary-100}{HTML}{f5f5f4}
\definecolor{primary-200}{HTML}{e7e5e4}
\definecolor{primary-300}{HTML}{d6d3d1}
\definecolor{primary-400}{HTML}{a8a29e}
\definecolor{primary-500}{HTML}{78716c}
\definecolor{primary-600}{HTML}{57534e}
\definecolor{primary-700}{HTML}{44403c}
\definecolor{primary-800}{HTML}{292524}
\definecolor{primary-900}{HTML}{1c1917}
\definecolor{primary-950}{HTML}{0c0a09}

\definecolor{accent}{HTML}{b45309} 
\definecolor{accent-50}{HTML}{fffbeb} 
\definecolor{accent-100}{HTML}{fef3c7}
\definecolor{accent-200}{HTML}{fde68a}
\definecolor{accent-300}{HTML}{fcd34d}
\definecolor{accent-400}{HTML}{fbbf24}
\definecolor{accent-500}{HTML}{f59e0b}
\definecolor{accent-600}{HTML}{d97706}
\definecolor{accent-700}{HTML}{b45309}
\definecolor{accent-800}{HTML}{92400e}
\definecolor{accent-900}{HTML}{78350f}
\definecolor{accent-950}{HTML}{451a03}


\begin{document}
\color{primary-950}

%\begin{center}
%\begin{minipage}{11cm}
%\begin{center}
\textbf {
  \fontsize{26pt}{32pt}\selectfont
  \color{primary-950}Maximiliano
  \color{accent}Hernandez Castillo
}
%\end{center}
%\end{minipage}
%\end{center}
\vspace{0.5cm}

Greetings.
\vspace{0.5cm}

I'm Max Hernandez, a software engineer with approximately three years of professional
experience. I've worked with Python backend scripts, NodeJS frontend applications, and a few
app designs incorporating graphic design fundamentals with mainly open source tools.


I am very confident working with Django to construct backend APIs. I've primarily written RESTFul
APIs, worked with MySQL and PostgreSQL relational databases, and have some experience with
related solutions like setting push notifications, adding cache using Redis or building
asynchronous tasks.


I've spent the last few years focusing on building frontend applications with React. I have
configured projects from scratch with Webpack and Rollup. I've created websites, single-page
applications, and NodeJS packages. I believe I am adept in HTML5, CSS, and vanilla Javascript.
I also have good experience with Linux systems, configuration, and bash scripting. I have basic
understanding of graphic design. I have some experience designing frontend apps with Inkscape,
Gimp, and Figma. I also have experience working in Agile environments.


Thank you for your attention and time. I'm looking forward to learn more about the position, and I
would welcome the chance to provide insight into my knowledge and experience.
\vspace{0.5cm}

Best regards.
\vspace{0.5cm}

{
  \setlength{\tabcolsep}{0pt}
  \begin{supertabular}{l}
    \href{ {{ url }} }{\faIcon{link} {{ url }} } \\
    \href{ mailto:{{ email }} }{\faIcon{envelope} {{ email }} } \\
    \faIcon{globe-americas} {{ formatedLocation }}
  \end{supertabular}
}


\end{document}